OpenMPIR

### 2017-09-08 paper.tex
Updated health plot, added clangs stacksize

The Intel compiler required increasing the stack size for \texttt{Fibonacci} and
\texttt{FFT}. The implementation seemed to use significantly more stack space
than the others, requiring setting \texttt{OMP\_STACKSIZE} to \texttt{256M} for
computing the 42nd Fibonacci number. \texttt{FFT} ran with an increase to
\texttt{16M}.

>>>>

The Intel compiler required increasing the stack size for \texttt{Fibonacci} and
\texttt{FFT}. The implementation seemed to use significantly more stack space
than the others, requiring setting \texttt{OMP\_STACKSIZE} to \texttt{256M} for
computing the 42nd Fibonacci number. \texttt{FFT} ran fine with an increase to
\texttt{16M}. Clang required a similar increase in \texttt{OMP\_STACKSIZE} for
\texttt{SparseLU}, needing to be increased to \texttt{64M} to avoid stack
overflows. GCC and the Tapir implementation required no such modifications. 
>>>>>>> Updated health plot, added clangs stacksize
